European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-01 manuscript/manuscript.qmd
Add 2nd para

>>>>

The results, presented in @tbl-results-fiscal, suggest that our finding that closer relations with the US, rather than European powers, are associated with fewer IMF conditions also applies to the *fiscal* subset of conditions. This also echoes @guimaraes2021, who note that political alignment with the US reduces the number of fiscal conditions, although they do not control for European influence. Nevertheless, a caveat is that these findings should not be interpreted as evidence that US influence reduces the *stringency* of fiscal conditionality, as our results on the required fiscal adjustment (RFA) are inconclusive, again similar to the results reported by @guimaraes2021. Also, one should note that the data for fiscal conditions are available only from 1999 onwards. When merged to our data, the number of observations is extremely limited ($N \approx 30$) and should not be over-interpreted.
